% Copyright 2007 TeX Users Group.
% You may freely use, modify and/or distribute this file.
\font\tir=tir at 10pt

\input texnansi

\tir

\noindent
{\bf It is important to be able to access all characters in a text font}

\vskip .1in

\noindent
This file assumes: 
(i) You have the Times-Roman font (Type 1 format of course) installed;
(ii) Type 1 fonts are enabled (i.e. ATM installed and running);
(ii) Your DVIWindo is set up to reencode text fonts to TeX 'n ANSi encoding,
That is, you have a line of the form ENCODING=texnansi in the [Environment]
section of dviwindo.ini (in the Windows directory).

Ligatures: fi fl ff ffi ffl.  
No other {\TeX} system in Windows can show {\it any\/} of the f-ligatures 
in an ordinary text font like Times-Roman.
On the Macintosh, Textures can show the fi and fl ligatures but {\it not\/}
the ff, ffi, and ffl ligatures.

Newton's notation for derivatives needs `dotaccent' in the text font
($\dot{x}$).
No other {\TeX} system in Windows can show this accent!  
Hence you have to use Leibnitz notation for derivatives.

For composite characters based on the letter `i'
you need to have `dotlessi' if you want other than the
basic ones: \`\i \'\i \~\i \"\i \~\i.
So you can't make \v\i \r\i \H\i \u\i in those system!

Actually, in all other {\TeX} systems for Windows you can't
get at the accents 
`caron' (\char20), `ring' (\char23), `hungarumlaut' (\char6), 
`breve' (\char21), `ogonek' (\char7) , `dotaccent' (\char5)
anyway.

Other {\TeX} systems for Windows can't access ready-made composites
`Lslash' (\char128), `lslash' (\char144), `Zcaron' (\char141),
`zcaron' (\char157).

Other {\TeX} systems for Windows can't access some other glyphs
in text fonts like `minus' (\char143) and `fraction' (\char9).

% Some (15) other glyphs one might have wanted to see here: 
% Zcaron, zcaron, Lslash, lslash
% dotlessi, caron, ring, dotaccent, hungarumlaut, breve, ogonek 
% fi, fl, fraction, minus.

In addition Textures cannot access 
`Zcaron' (\char141), `zcaron' (\char157),
`Yacute' (\char221), `yacute' (\char253),
`Scaron' (\char138), `scaron' (\char154),
`Eth' (\char208), `eth' (\char240),
`Thorn' (\char222), `thorn' (\char254),
`multiply' (\char215), `brokenbar' (\char166),
`onequarter' (\char188), `onehalf' (\char189), `threequarters' (\char190), 
`onesuperior' (\char185), `twosuperior' (\char178), `threesuperior' (\char179)

% Some (21) other glyphs one might have wanted to see here: 
% Zcaron, zcaron, Lslash, lslash, Yacute, yacute, Scaron, scaron
% Eth, eth, Thorn, thorn, minus, multiply, brokenbar
% onequarter, onehalf, threequarters, onesuperior, twosuperior, threesuperior

\end
