% Copyright 2007 TeX Users Group.
% You may freely use, modify and/or distribute this file.

% hello_CM.tex --- LaTeX 2e sample for Computer Modern

\documentclass{article}

% \usepackage{type1cm}	% see notes at end on Type1CM package

\begin{document}

\hrule \vskip 2mm

``Hello World!'' --- $\alpha = \Gamma -\sqrt{x^2+y^2}$.

\vskip 2mm

{\bf Bold}. {\it Italic}. {\tt Fixed width}. {\sf Sans Serif}.

% \vskip 2mm

% ,,German`` ``English'' << French >>  >>Swedish<<  (not available in CM)

\vskip 2mm

The difficult first flight afflicts the efflux differently.

\vskip 2mm

na\"\i ve; belov\`ed; prot\'eg\'e; r\^ole co\"ordinator; souffl\'es, 

\vskip 2mm

cr\^epes, and p\^at\'es; \AE sop's \OE uvres, \AA ngstrom, Stra\ss e.

\vskip 2mm \hrule \vskip 2mm

\noindent
As far as \TeX\ is concerned, CM fonts in ATM compatible Adobe Type~1 format
(`PostScipt' or `ATM' fonts ) are the same as CM fonts in bitmapped PK font
format, since \TeX\ itself only cares about TFM meric files.  Consequently,
there are no changes needed in your \TeX\ source file when you use them.

The Type~1 versions of the CM fonts do have the ability to easily scale
(in addition to providing different fonts for different design sizes).
This means you can use `in-between' sizes like CMR17 at 15pt.  David
Carlisle's Type1CM package takes advantage of this. It may be found at:

\vskip 2mm

{\sf /tex-archive/macros/latex/contrib/supported/type1cm} on CTAN.

\vskip 2mm

\noindent Read `type1cm.txt' in that directory for details.

CM `text' fonts have fixed encoding (character layout) called 
`TeX text' or OT1.  \LaTeX\ 2e uses OT1 encoding unless you tell it otherwise.

NOTE: the setting of `Font $>$ Encoding' in DVIWindo does not affect CM fonts 
since CM `text' fonts have to be treated as pi/symbol/decorative/math fonts
in order to prevent reencoding to platform specific layout (Macintosh
standard roman or Windows ANSI).

If you need hyphenation in languages using accented and special characters
consider the European Modern font set which has ready-made accented chars.
The basic characters in European Modern are the same as those in CM.
\LaTeX\ 2e support for EM fonts may be found in the `em' package.

\vskip 2mm \hrule

\end{document}

